# SOURCE FILES AND PROVENANCE {#sec-source}

```{r}
#| include: false
source("_setup.R")
```

## Verification

This document was generated from popPK version v`r poppk_version` without refitting any model. Before rendering, the version's provenance record was verified: its sidecar hash matched and every output file matched its recorded hash; the results database was read with its payload hash checked. Latest automated \gls{QC} suite run: `r qc_text`. \gls{QC} status recorded in the provenance record: **`r spec$qc$status`**`r if (!is.null(spec$qc$reviewer)) sprintf(" (reviewer: %s, %s)", spec$qc$reviewer, spec$qc$reviewed_date %||% "") else ""`.

## Model Trail and Final Model

As recorded in the provenance record: each run's \gls{OFV}, its difference from the parent run (dOFV), the number of estimated parameters and whether the covariance step succeeded. Run descriptions are in the model development table (@sec-tables).

```{r}
#| label: tbl-trail
#| tbl-cap: "Model trail recorded in the provenance record"
report_table(spec_model_trail(spec), align = c("l", "l", "r", "r", "r", "l"))
```

Final model: **`r spec$final_model$run_id`** (`r toupper(spec$final_model$est)`, \gls{OFV} `r sprintf("%.2f", spec$final_model$objf)`). Selection rationale recorded by the analysis: `r md_escape(spec$final_model$rationale %||% "--")`

```{r}
#| label: tbl-checks
#| tbl-cap: "Acceptance checks of the final model"
report_table(spec_acceptance_checks(spec), align = c("l", "l", "l"))
```

Caveats recorded in the provenance record: `r caveats <- unlist(spec$diagnostics$caveats); if (length(caveats)) md_escape(paste(caveats, collapse = "; ")) else "none"`.`r if (!is.null(spec$diagnostics$notes)) paste0(" Diagnostic notes: ", md_escape(spec$diagnostics$notes)) else ""`

## Provenance

```{r}
#| label: tbl-provenance
#| tbl-cap: "Provenance of the reported results"
report_table(tibble::tribble(
  ~Item, ~Value,
  "Analysis version", sprintf("popPK v%d (%s)", poppk_version, spec$script_dir),
  "Source data", spec$data$source_file$path,
  "Source data hash", spec$data$source_file$hash,
  "Model dataset hash", spec$data$hash$combined %||% "--",
  "Results database", spec$data$poppk_db$path,
  "Database payload hash", spec$data$poppk_db$payload_hash,
  "Scripts combined hash", spec$scripts_combined_hash,
  "Analysis run", spec$data$poppk_db$generated_at %||% "--",
  "Provenance record", sprintf("spec/poppk/v%d.yaml (generated %s)", poppk_version, spec$generated_at),
  "R version", spec$r_version %||% "--"
), align = c("l", "l"))
```

## Source Data

```{r}
#| label: tbl-dataset
#| tbl-cap: "Model dataset as stored in the results database"
report_table(tibble::tribble(
  ~Item, ~Value,
  "Source file", spec$data$source_file$path,
  "Model dataset", md_escape(spec$data$model_data %||% "--"),
  "Participants", as.character(data_sum$n_subjects),
  "Observation records", as.character(data_sum$n_obs),
  "Dose records", as.character(data_sum$n_doses),
  "Doses", sprintf("%s %s", paste(data_sum$doses, collapse = ", "), u$dose),
  "Observation time range", sprintf("%s to %s %s", data_sum$time_range[1], data_sum$time_range[2], u$time),
  "Other columns", if (length(data_sum$other_cols)) md_escape(paste(data_sum$other_cols, collapse = ", ")) else "none",
  "Data validation report", validation_report()
), align = c("l", "l"))
```

## Fit Archives

The nlmixr2save archives of every fit, as recorded in the provenance record.

```{r}
#| label: tbl-archives
#| tbl-cap: "Fit archives with their hashes"
report_table(spec_fit_archives(spec), align = c("l", "l", "l"))
```

## Packages

```{r}
#| label: tbl-packages
#| tbl-cap: "Package versions recorded in the provenance record"
pk <- spec$packages %||% list()
report_table(tibble::tibble(Package = names(pk), Version = unlist(pk, use.names = FALSE)), align = c("l", "l"))
```

## Run Logs

```{r}
#| label: tbl-logs
#| tbl-cap: "Latest run log of each script"
report_table(log_table(), align = c("l", "l", "l"))
```

## Electronic File Manifest

```{r}
#| label: tbl-manifest
#| tbl-cap: "Analysis scripts and outputs with their hashes"
manifest <- dplyr::bind_rows(
  tibble::tibble(Type = "Script", File = file.path(spec$script_dir, names(spec$script_hashes)),
                 Hash = unlist(spec$script_hashes)),
  tibble::tibble(Type = "Table", File = vapply(spec$outputs$tables, `[[`, "", "path"),
                 Hash = vapply(spec$outputs$tables, `[[`, "", "hash")),
  tibble::tibble(Type = "Table object",
                 File = unlist(lapply(spec$outputs$tables, function(e) e$display_rds$path)),
                 Hash = unlist(lapply(spec$outputs$tables, function(e) e$display_rds$hash))),
  tibble::tibble(Type = "Figure", File = vapply(spec$outputs$figures, `[[`, "", "path"),
                 Hash = vapply(spec$outputs$figures, `[[`, "", "hash")),
  tibble::tibble(Type = "Figure object",
                 File = unlist(lapply(spec$outputs$figures, function(e) e$display_rds$path)),
                 Hash = unlist(lapply(spec$outputs$figures, function(e) e$display_rds$hash)))
)
report_table(manifest, align = c("l", "l", "l"))
```
